%-------------------------
% Resume in Latex
% Author : Adam Skriver
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\vfill

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Adam Skriver} \\ \vspace{1pt}
    \small \href{https://nineriver.ca}{\underline{nineriver.ca}} $|$
    \href{https://www.linkedin.com/in/adam-skriver/}{\underline{LinkedIn}} \\
    Calgary, AB, Canada
\end{center}


%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    Systems Specialist with 17+ years experience bridging the gap between complex technical infrastructure and business goals. Expert in Data \& Application Enablement, transforming legacy workflows into efficient, automated systems (Windchill PLM, AWS/Hybrid Cloud). Proven track record of leading cross-functional teams, translating technical requirements for non-technical stakeholders, and driving user adoption. Passionate about data governance and process automation, seeking to leverage deep expertise in systems integration to enable team success at a forward-thinking organization.
    }}
  \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DeVry University}{Calgary, AB}
      {Bachelor of Science in Electronics Engineering Technology}{Aug. 2000 -- Oct. 2003}
      \resumeItemListStart
        \resumeItem{Applied technical degree focused on systems integration, control systems, and practical implementation}
        \resumeItem{Core studies: Critical Thinking, Systems Design, Circuit Design, Control Systems, Signal Processing, Digital Systems, Technical Communication, Systems Administration}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Principal Consultant / Infrastructure Systems Architect}{Nov. 2024 -- Present}
      {NineRiver Technologies}{Calgary, AB}
      \resumeItemListStart
        \resumeItem{Architected a secure, cloud-agnostic hybrid network connecting Vultr edge nodes and on-premise Proxmox clusters via a WireGuard site-to-site VPN, ensuring data sovereignty and low-latency access.}
        \resumeItem{Designed modular infrastructure strategies to avoid vendor lock-in, evaluating Azure and AWS ecosystems to advise on cost-optimized, flexible deployment patterns.}
        \resumeItem{Defining Infrastructure-as-Code (Terraform) roadmaps to transition manual configurations into reusable modules, establishing standards for state management and disaster recovery.}
        \resumeItem{Building data-driven monitoring solutions (Prometheus/Grafana) to provide visibility into system health, enabling proactive maintenance rather than reactive support.}
      \resumeItemListEnd

    \resumeSubheading
      {Electronic Engineering Technologist}{Oct. 2007 -- Dec. 2024}
      {Laversab Inc.}{Houston, TX / Remote}
      \resumeItemListStart
        \resumeItem{Leveraged enterprise PLM tools (Windchill) to manage complex aviation test equipment configurations, ensuring strict adherence to data governance and regulatory standards.}
        \resumeItem{Collaborated across electrical, firmware, and mechanical teams to integrate diverse technical requirements into the PLM environment, resolving design conflicts to maintain project schedules.}
        \resumeItem{Maintained data integrity for product specifications and change orders (ECOs), ensuring accurate documentation throughout the product lifecycle.}
        \resumeItem{Adapted complex engineering workflows to fit within established system constraints, troubleshooting integration issues to ensure successful product data management.}
      \resumeItemListEnd

    \resumeSubheading
      {Co-Owner \& Technical Systems Lead}{Jan. 2010 -- Apr. 2022}
      {Coastal Cake Company}{Vancouver Island, BC}
      \resumeItemListStart
        \resumeItem{Built integrated business systems connecting Google Workspace, Lightspeed POS, QuickBooks, and Squarespace while maintaining full-time engineering role}
        \resumeItem{Developed ETL workflows and automated data pipelines for order processing, inventory management, and financial reporting}
        \resumeItem{Implemented data quality validation ensuring accuracy of customer orders, inventory levels, and financial transactions}
        \resumeItem{Provided technical guidance and training to non-technical staff, creating documentation for integrated systems and procedures}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Portfolio Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{GalleryMD} $|$ \emph{Docker, Nginx, Security Architecture} $|$ \href{https://gallerymd.9river.online}{\underline{gallerymd.9river.online}}}{2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed secure document discovery system with remote gateway implementation demonstrating enterprise security patterns}
            \resumeItem{Implemented production-grade deployment with reverse proxy configuration and automated content workflows}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{RecipeFlow} $|$ \emph{Data Engineering, Python, Algorithmic Logic}}{2024 -- Present}
          \resumeItemListStart
            \resumeItem{Engineered a data transformation pipeline to migrate static legacy datasets into dynamic, parameter-driven models, enabling algorithmic scaling of ingredients based on variables like altitude and production volume.}
            \resumeItem{Architected a self-hosted storage solution (PostgreSQL/S3) to centrally manage unstructured rich media and relational data, ensuring long-term data accessibility and sovereignty.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{HeartsAndStars} $|$ \emph{Full-Stack Web Application}}{2025}
          \resumeItemListStart
            \resumeItem{Architected full-stack task management system using Python/Django and PostgreSQL on Proxmox platform, demonstrating rapid proof-of-concept development within secure infrastructure}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Competencies}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Enterprise Systems}{: Windchill PLM (7 years), Configuration Management, Data Governance, Lifecycle Management, Cross-functional Collaboration, Stakeholder Management} \\
     \textbf{Cloud \& Infrastructure}{: AWS (Cloud Practitioner 11/2025), Azure, Terraform (cert in progress), Kubernetes (learning), Nginx, Linux (30 years)} \\
     \textbf{Data \& Analytics}{: SQL, Excel (advanced automation), ETL workflows, Data quality management, Business Intelligence integration, Power BI (learning)} \\
     \textbf{DevOps \& Automation}{: Git/GitHub, GitOps, CI/CD Pipelines, Infrastructure-as-Code, Bash/PowerShell Scripting, Monitoring (Uptime Kuma, Prometheus/Grafana)} \\
     \textbf{Development Tools}{: VS Code, Python (learning), JavaScript, YAML/JSON, Database Design (PostgreSQL, SQLite)} \\
     \textbf{Business Systems}{: Google Workspace, POS Systems, ERP/QuickBooks, Workflow Automation, System Integration} \\
     \textbf{AI \& Emerging Tech}{: Ollama, Open WebUI, GitHub Copilot, LocalLLM, AI Workflow Automation}
    }}
 \end{itemize}


%-----------CERTIFICATIONS-----------
\section{Certifications \& Professional Development}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Completed}{: AWS Certified Cloud Practitioner (November 2025)} \\
     \textbf{In Progress}{: AWS Certified Developer – Associate, Microsoft Certified: Azure Developer Associate  (Target Q4 2025)} \\
     \textbf{Planned}{: HashiCorp Terraform Associate (Q1 2026)}
    }}
 \end{itemize}


%-----------SECURITY CLEARANCE-----------
\section{Security Clearance Eligibility}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Canadian citizen with stable 22-year employment history. Prepared to begin enhanced security clearance process immediately upon offer. Comprehensive documentation (10+ years residence, employment, references) ready for expedited processing.
    }}
 \end{itemize}


%-----------ADDITIONAL INFO-----------
\section{Additional Information}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Location}{: Calgary, AB -- Available for hybrid or on-site work arrangements} \\
     \textbf{Availability}{: Available Immediately — Open to Contract-to-Hire.}
    }}
 \end{itemize}

\vfill

%-------------------------------------------
\end{document}
